Finding Quality Issues in SKOS Vocabularies

### 2012-04-03 analysis.tex
added stw mapping description

The basic statistical properties of our vocabulary selection are summarized in Table~\ref{tab:vocabs}: the number of concepts and authoritative concepts, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations involving concepts (\texttt{Concept Labels}), all asserted semantic relations, as well as the number of concept schemes. From these properties we can, for instance, already see that approximately 3,000 \texttt{DBpedia Categories} concepts do not have labels (e.g., \url{Category:South_Korean_social_scientists}), which indicates that the same amount of Wikipedia categories misses natural language descriptions.

@@

% LABELING AND DOCUMENTATION ISSUES
We found labeling and documentation issues in all vocabularies.
% Omitted or Invalid Language Tags
\texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} omit language tags with their labeling properties, \texttt{LCSH} with the \texttt{skos:note} property. \texttt{STW} does not use language tags with 2 instances of \texttt{skos:definition}.
% Incomplete Language Coverage
\texttt{AGROVOC} covers 25 languages but no single concept is labeled in all languages, in \texttt{Meketre} all concepts have English but only some of them French labels assigned. STW, which is expressed mainly in English and German, has many concepts with incomplete language coverage because it (i) links to non-authoritative concepts that are only labeled in German and (ii) uses the private, but valid language tag \texttt{x-other} with some of its concept labels.
%The reasons for the high number of concepts with incomplete language coverage in \texttt{STW} are that many concepts (i) link to non-authoritative concepts that are only labeld in German and (ii) lack labels tagged with the private, but valid language tag \texttt{x-other} that few concepts pull in. 
% Undocumented Concepts
\texttt{Geonames}, which is an ontology including a concept scheme of ``feature codes'', is the only vocabulary in our dataset, which has at least one documentation property assigned to all of its concepts. All other vocabularies have a significant number of undocumented concepts.
% Label Conflicts
We also detected possible label issues in half of the vocabularies. \texttt{PXV}, for instance, uses the string ``primary peroxisomal enzyme deficiency'' with two concepts in the same concept scheme, but once with a \texttt{skos:prefLabel} and another time with a \texttt{skos:altLabel} property. For every concept in \texttt{NAICS}, a \texttt{rdfs:label} as well as a \texttt{skosxl:prefLabel} is defined. However, objects of the \texttt{prefLabel} triples are plain literals which seems to be a misunderstanding of SKOS-XL by the vocabulary creators. Thus, this information is not processed and no conflicts are found.
%An example from AGROVOC is ``sziv\'{a}rv\'{a}nyos pisztr\'{a}ng'', which is used as \texttt{skos:altLabel} with two different concepts.

>>>>

The basic statistical properties of our vocabulary selection are summarized in Table~\ref{tab:vocabs}: the number of concepts and authoritative concepts, all \texttt{skos:prefLabel}, \texttt{skos:altLabel}, and \texttt{skos:hiddenLabel} relations involving concepts (\texttt{Concept Labels}), all asserted semantic relations, as well as the number of concept schemes. From these properties we can, for instance, already see that approximately 3,000 \texttt{DBpedia Categories} concepts do not have labels (e.g., \url{Category:South_Korean_social_scientists}), which indicates that the same amount of Wikipedia categories misses natural language descriptions. \textcolor{red}{The vocabularies have been received as bulk downloads from the respective websites or directly from the creators. We further added available mapping files to the base \texttt{STW} vocabulary to accurately measure the number of out-links.}

@@

% LABELING AND DOCUMENTATION ISSUES
We found labeling and documentation issues in all vocabularies.
% Omitted or Invalid Language Tags
\texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} omit language tags with their labeling properties, \texttt{LCSH} with the \texttt{skos:note} property. \texttt{STW} does not use language tags with 2 instances of \texttt{skos:definition}.
% Incomplete Language Coverage
\texttt{AGROVOC} covers 25 languages but no single concept is labeled in all languages, in \texttt{Meketre} all concepts have English but only some of them French labels assigned. STW, which is expressed mainly in English and German, has many concepts with incomplete language coverage because it (i) links to non-authoritative concepts that are only labeled in German and (ii) uses the private, but valid language tag \texttt{x-other} with some of its concept labels.
%The reasons for the high number of concepts with incomplete language coverage in \texttt{STW} are that many concepts (i) link to non-authoritative concepts that are only labeld in German and (ii) lack labels tagged with the private, but valid language tag \texttt{x-other} that few concepts pull in. 
% Undocumented Concepts
\texttt{Geonames}, which is an ontology including a concept scheme of ``feature codes'', is the only vocabulary in our dataset, which has at least one documentation property assigned to all of its concepts. All other vocabularies have a significant number of undocumented concepts.
% Label Conflicts
We also detected possible label issues in half of the vocabularies. \texttt{PXV}, for instance, uses the string ``primary peroxisomal enzyme deficiency'' with two concepts in the same concept scheme, but once with a \texttt{skos:prefLabel} and another time with a \texttt{skos:altLabel} property. \textcolor{red}{For every concept in \texttt{NAICS}, a \texttt{rdfs:label} as well as a \texttt{skosxl:prefLabel} is defined. However, objects of the \texttt{prefLabel} triples are plain literals which seems to be a misunderstanding of SKOS-XL by the vocabulary creators. Thus, this information is not processed and no conflicts are found.}
%An example from AGROVOC is ``sziv\'{a}rv\'{a}nyos pisztr\'{a}ng'', which is used as \texttt{skos:altLabel} with two different concepts.

### 2012-04-03 criteria.tex
added stw mapping description

% Origin and rationale
SKOS defines a set of properties that link resources with RDF Literals, which are plain text natural language strings with an optional language tag. This includes the labeling properties \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof. Literals should be tagged consistently~\cite{Vrandecic2010}, because omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could unintentionally limit the result set of language-dependent queries.
% Function defintion
A SKOS vocabulary can be checked for omitted and invalid language tags by iterating over all resources in $IR$ and finding those that have labeling or documentation property relations to plain literals in $LV$ with missing or invalid language tags, i.e., tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.

>>>>

% Origin and rationale
SKOS defines a set of properties that link resources with RDF Literals, which are plain text natural language strings with an optional language tag. This includes the labeling properties \textcolor{red}{\texttt{rdfs:label}}, \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof. Literals should be tagged consistently~\cite{Vrandecic2010}, because omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could unintentionally limit the result set of language-dependent queries.
% Function defintion
A SKOS vocabulary can be checked for omitted and invalid language tags by iterating over all resources in $IR$ and finding those that have labeling or documentation property relations to plain literals in $LV$ with missing or invalid language tags, i.e., tags that are not defined in RFC3066\footnote{RFC 3066: Tags for the Identification of Languages \url{http://www.ietf.org/rfc/rfc3066.txt}}.
